Interval Probability for Fuzzy Quantum Theories

### 2016-07-02 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} update the counterexample...

@@

We have enough examples for quantum interval-valued probability measure,
it is instructive to understand the conditions by studying a measure
which is not a quantum interval-valued probability measure.

\begin{example}[Not three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
as before. Let
\begin{eqnarray*}
\bar{\mu}(\mathbb{0}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1}) & = & \necess\textrm{ ,}\\
\bar{\mu}(\proj{0}) & = & \necess\textrm{ ,}\\
\bar{\mu}(\proj{\ps}) & = & \necess\textrm{ ,}\\
\bar{\mu}(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
\bar{\mu}(1-\proj{0}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
$\bar{\mu}$ is not a quantum interval-valued probability measure. To verify
this fact, we first consider an orthonormal basis
\begin{eqnarray*}
\ket{\psi_{0}} & = & \frac{1}{\sqrt{2}}\ket{1}+\frac{1}{\sqrt{2}}\ket{2}\\
\ket{\psi_{1}} & = & \frac{1}{\sqrt{3}}\ket{0}-\frac{1}{\sqrt{3}}\ket{1}+\frac{1}{\sqrt{3}}\ket{2}\\
\ket{\psi_{2}} & = & \sqrt{\frac{2}{3}}\ket{0}+\frac{1}{\sqrt{6}}\ket{1}-\frac{1}{\sqrt{6}}\ket{2}
\end{eqnarray*}
However,

\begin{eqnarray*}
 &  & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\bar{\mu}\left(1-\proj{\psi_{2}}\right)=\unknown\\
 & \nsubseteq & \imposs+\imposs=\bar{\mu}\left(\proj{\psi_{1}}\right)+\bar{\mu}\left(\proj{\psi_{2}}\right)\textrm{ .}
\end{eqnarray*}
\qed\end{example}

\yutsung{For \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
are there any quantum interval-valued probability measures do not
come from quantum probability measures?}

>>>>

Although $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ maps every
quantum probability measure to a quantum interval-valued probability
measure, there is a quantum \emph{$\mathscr{I}$}-interval-valued
probability measure which does not come from a quantum probability
measure.

\begin{example}[Three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
as before. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(1-\proj{0})=\bar{\mu}(1-\proj{\ps}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\bar{\mu}(P)=\iota\left(\mu(P)\right)$ for some $\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j}q_{j}=1$ and $q_{j}>0$. By
equation (\ref{eq:probability-zero-on-states}),
we have $\rho=\proj{2}$. However, 
\[
\iota\left(\mu(\proj{2})\right)=\necess\ne\unknown=\bar{\mu}(P)\textrm{ .}
\]
\qed\end{example}

@@
